A fast unified model for parsing and sentence understanding

### 2016-03-15 writing/hard_stack_paper/paper.tex
Typo / diction fixes; be stronger in the anti-attention-model paragraph

Even though NLI is framed as a relatively simple three-way classification task, it is nonetheless an effective way of evaluating the ability of some model to extract broadly informative representations of sentence meaning. In order for a model to reliably perform well on NLI across a range of sentence types and text genres, it must be able to represent and reason with all of the core phenomena of natural language semantics, including quantification, coreference, scope, and several types of ambiguity.

@@

We evaluate four models on the SNLI task. Each uses 300d hidden states:
\begin{itemize}
\item A baseline LSTM model (similar to that of \citealt{snli:emnlp2015}) that uses the same classifier architecture as our models, but encodes sentences using a single layer LSTM RNN sequence model.
\item The minimal SPINN-NP-NT (\textit{no parsing, no tracking}) model, which uses transitions from an external parser, and has no tracking LSTM to inform semantic composition. This model is strictly equivalent to a TreeLSTM.
\item The full SPINN-NP model, which adds in the use of a tracking LSTM to guide composition, making it a tree-sequence hybrid.
\item The full SPINN model, which makes its own parsing decisions, and does not depend on an external parser at test time, making it slightly weaker but a practical choice in applied settings.
\end{itemize}

We compare our models against a range of baselines, including the strongest published non-neural network-based result from \cite{snli:emnlp2015}, a set of previous neural network models built around sentence encoders, and a set of models built around soft attention architectures. We should note that these attention-based models are by far the strongest published on SNLI to date, but we do not wish to compare our model with those models directly. SNLI was originally presented as an evaluation and development task for sentence encoding models, on the premise that sentence encoding models that do well on SNLI capture sentence meaning in a general sense, and are well suited to use on a range of NLP tasks. We follow that approach, and focus on sentence encoding, rather than on attentional models, which are much more narrowly adapted to the sentence-pair structure of SNLI examples.

>>>>

Even though NLI is framed as a relatively simple three-way classification task, it is nonetheless an effective way of evaluating the ability of some model to extract broadly informative representations of sentence meaning. In order for a model to perform reliably well on NLI across a range of sentence types and text genres, it must be able to represent and reason with all of the core phenomena of natural language semantics, including quantification, coreference, scope, and several types of ambiguity.

@@

We evaluate four models on the SNLI task. Each uses 300d hidden states:
\begin{itemize}
\item A baseline LSTM model (similar to that of \citealt{snli:emnlp2015}) that uses the same classifier architecture as our models, but encodes sentences using a single layer LSTM-RNN sequence model.
\item The minimal SPINN-NP-NT (\textit{no parsing, no tracking}) model, which uses transitions from an external parser, and has no tracking LSTM to inform semantic composition. This model is equivalent to a TreeLSTM \cite{tai2015improved}.
\item The SPINN-NP model, which includes a tracking LSTM which guides composition, making it a hybrid tree-sequence model.
\item The full SPINN model, which makes its own parsing decisions, and does not depend on an external parser at test time, making it slightly weaker but a practical choice in applied settings.
\end{itemize}

We compare our models against a range of baselines, including the strongest published non-neural network-based result from \cite{snli:emnlp2015}, a set of previous neural network models built around sentence encoders, and a set of models built around soft attention architectures. We should note that these attention-based models are by far the strongest published on SNLI to date, but we do not wish to compare our model with those models directly. SNLI was originally presented as an evaluation and development task for sentence encoding models, on the premise that sentence encoding models that do well on SNLI capture sentence meaning in a general sense, and are well suited to use on a range of NLP tasks. The attentional models are narrowly adapted to the sentence-pair structure of SNLI examples and cannot act as such general sentence encoders. We focus on models which do support general sentence encoding in our analysis.
